Constraint Programming - Inside Gecode

### 2014-05-03 paper.tex
added pseudo code for LDS
added pseudo code for depth-first search

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{amsfonts}
\usepackage[pdftex]{graphicx}
\graphicspath{{../png/}}
\DeclareGraphicsExtensions{.png}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{algorithmic}
\usepackage{array}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{fixltx2e}
\usepackage{stfloats}
\usepackage{url}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{stmaryrd}
\usepackage{bbding}
\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usepackage{listings}
\usepackage{color}

@@

	\subsubsection{Depth-First Search}
	The Depth-First Search is a good point to start, as it was also historical the first developed one. The idea behind this search algorithm is that every possible combination of variables is examined. Obviously in its basic form it can not be applied to problems with inifinite domains; for problems with such variable domains it is necessary to use for example a Branch-and-Bound Search.

@@

	By stopping the search after one feasible solution is found the algorithm the search can often be accelerated. Although this slightly modified version is not complete anymore, in practice it is in some areas sufficient to know just one valid solution.

	\subsubsection{Depth-First Search with Optimization}
	If in the constraint programming is a certain objective is defined which should be either minimized or maximized a modified version of the Depth-First Search can be applied. The only difference is that it evalutes the objective function for every found solution concerning the constraints and stores during the search only the best one. To accelerate the search after one solution is already found it is possible to add an additional constraint which defines, that the new objective must be greater than the one related to the best solution till that point. Through this enhancement it is possible to prune even more sub trees and therefore to get the desired result faster.

@@

	\subsubsection{Limited Discrepancy Search}
	Limited Discrepancy Search falls into the category of Best-First searches and was first mentioned by Harvey and Ginsberg in \cite{limitedDiscrepancy} and it depends on some heurisitics for the tree, which is determined through branching strategies. The basic concept is that during a chronological backtrack search a wrong turn close to the root is first of all very expensive and second heurisitics work worse the farther away from the solution they are. Consequently, in a chronological backtrack search the worst decisions are the most expensive ones. The Limited Discrepancy Search solves exactly this problem as it suggests to change rather the decisions made close to the root than the ones the search made later. The improvement ahead of a chronological backtrack were shown by experimental results and theoretical proven in \cite{limitedDiscrepancy}.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{amsfonts}
\usepackage[pdftex]{graphicx}
\graphicspath{{../png/}}
\DeclareGraphicsExtensions{.png}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{array}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{fixltx2e}
\usepackage{stfloats}
\usepackage{url}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{stmaryrd}
\usepackage{bbding}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usepackage{listings}
\usepackage{color}

@@

	\subsubsection{Depth-First Search}
	\begin{algorithm}
		\begin{algorithmic}
			\Function{DFS}{node}
				\If{$Goal(node)$}
					\State \Return $node$
				\EndIf
				\State $s \gets Successors(node)$
				\If{$Null(s)$}
					\State \Return $nil$
				\EndIf
				\State $result \gets DFS(Left(s))$
				\If{$result \ne nil$}
					\State \Return $result$
				\Else
					\State \Return $DFS(Right(s))$
				\EndIf
			\EndFunction
		\end{algorithmic}
		\caption{Depth-first search in a binary search tree for one feasible solution, without constraint propagation}
	\end{algorithm}

	The Depth-first search is a good point to start, as it was also historical the first developed one. The idea behind this search algorithm is that every possible combination of variables is examined. Obviously in its basic form it can not be applied to problems with inifinite domains; for problems with such variable domains it is necessary to use for example a Branch-and-Bound Search. Sometimes the Depth-First Search is also referred to as chronological backtrack search.

@@

	By stopping the search after one feasible solution is found the algorithm the Depth-first search can often be accelerated. Although this slightly modified version is not complete anymore, in practice it is in some areas sufficient to know just one valid solution.

	\subsubsection{Depth-First Search with Optimization}
	If in the constraint programming is a certain objective is defined which should be either minimized or maximized a modified version of the Depth-first search can be applied. The only difference is that it evalutes the objective function for every found solution concerning the constraints and stores during the search only the best one. To accelerate the search after one solution is already found it is possible to add an additional constraint which defines, that the new objective must be greater than the one related to the best solution till that point. Through this enhancement it is possible to prune even more sub trees and therefore to get the desired result faster.

@@

	\subsubsection{Limited Discrepancy Search}
	Limited Discrepancy Search falls into the category of Best-first searches and was first mentioned by Harvey and Ginsberg in \cite{limitedDiscrepancy} and it depends on some heurisitics for the tree, which is determined through branching strategies. The basic concept is that during a chronological backtrack search a wrong turn close to the root is first of all very expensive and second heurisitics work worse the farther away from the solution they are. Consequently, in a chronological backtrack search the worst decisions are the most expensive ones. The Limited Discrepancy Search solves exactly this problem as it suggests to change rather the decisions made close to the root than the ones the search made later. The improvement ahead of a chronological backtrack were shown by experimental results and theoretical proven in \cite{limitedDiscrepancy}.

	\begin{algorithm}
		\begin{algorithmic}
			\Function{$LDSProbe$}{$node$, $k$}
				\If{$Goal(node)$}
				    \State \Return $node$
				\EndIf
				\State $s \gets Successors(node)$
				\If{$Null(s)$}
					\State \Return $nil$
				\EndIf
				\If{$k = 0$}
					\State \Return $LDSProbe(Left(s), 0)$
				\Else
					\State $result \gets LDSProbe(Right(s), k - 1)$
					\If{$result \ne nil$}
						\State \Return $result$
					\EndIf
					\State \Return $LDSProbe(Left(s), k)$
				\EndIf
			\EndFunction
		\end{algorithmic}
		\caption{Probe of Limited Discrepancy Search for a binary search tree from \cite{limitedDiscrepancy}, without constraint propagation}
	\end{algorithm}

	\begin{algorithm}
		\begin{algorithmic}			
			\Function{$LDS$}{$node$}
				\For{$x \gets 0\ \text{to maximum depth}$}
					\State $result \gets LDSProbe(node, x)$
					\If{$result \ne nil$}
						\State \Return $result$
					\EndIf
				\EndFor
			\EndFunction
		\end{algorithmic}
		\caption{Limited Discrepancy Search for a binary search tree from \cite{limitedDiscrepancy}, without constraint propagation}
	\end{algorithm}
